Scaffolder - Software for Microbial Genome Scaffolding.

### 2011-01-18 text/src/article.tex
Initial draft of implementation section

% }}}
% {{{ Background
\section*{Background}
 Text for this section.\cite{koon,oreg,khar,zvai,xjon,schn,pond,smith,marg,hunn,advi,koha,mouse}
% }}}
% {{{ Implementation
%%%%%%%%%%%%%%%%%%%%%%
\section*{Implementation}
  Text for this section \ldots
% }}}
% {{{ Results and Discussion

@@

% }}}
% {{{ Competing Interests
\section*{Authors contributions}
  The authors declare no competing interests.
% }}}
% {{{ Author Contributions
\section*{Authors contributions}

>>>>

% }}}
% {{{ Background
\section*{Background}
 Text for this section.
% }}}
% {{{ Implementation
\section*{Implementation}

Scaffolder is written in Ruby \cite{ruby-lang} using version 1.8.7. Unit and
ntegration tests use RSpec and Cucumber\cite{rspec}. The source code is
documented in-line using Yard\cite{yard} and the Unix manual pages are
generated using Ronn\cite{ronn}.

The sequence scaffold is defined in YAML\cite{yaml}. YAML is a machine
readable data format written using indentation of white space. YAML is designed
to be human readable which is ideal for manual editing of a genome scaffold.
Each stretch of sequence in the genome scaffold is defined as a list entry in
the YAML scaffold file. When parsing the scaffold file Scaffolder iterates over
each scaffold entry to create an instance of the Scaffolder::Region class.

The Region class is inherited by all types of sequence in the scaffold. The
Region provides helper methods common to the tasks in manipulating scaffold
sequence, subsequencing and reversing. In particular the region class has
a class annotation method\cite{class-annotations} which allows attributes in the
scaffold method to be defined in the class. This negates having to write
a custom method to deal with each scaffold variable.  Furthermore this makes
the process of transferring attributes from the scaffold file to each region
instance much simpler - each yaml attribute corresponds to a method call on the
instantiated class. The scaffold file effectively becomes a DSL for populating
the scaffold region instances while still maintaining the machine readable data
qualities of YAML.

The region class provides a sequence hook method. This method returns by
default the sequence corresponding to the fasta sequence defined by the source
tag which is then sublclassed or reversed if necessary. Subclasses of the region
class should override this method to provide custom functionality in
manipulating the source sequence. For example, the Scaffolder::Region::Sequence
class overrides the sequence method add any sequence inserts specified in the
scaffold file.

% }}}
% {{{ Results and Discussion

@@

% }}}
% {{{ Competing Interests
\section*{Authors contributions}
  The authors declare no competing interests.
% }}}
% {{{ Availability and Requirements
\section*{List of Abbreviations Used}

  \begin{description}
    \item[YAML:] YAML Ain't Markup Language\cite{yaml}
  \end{description}

% }}}
% {{{ Author Contributions
\section*{Authors contributions}
